IML Term project

### 2022-12-03 main_markdown.rmd
.

@@

>>>>

Looking at the correlation matrix as it was presented in the solutions to Exercise set 1, it is clear that the measurements of the same thing at different heights correlate, as do some of the radiation-related parameters.

# Calculate the correlation matrix
cm <- cor(npf[, endsWith(colnames(npf), ".mean")])
# Remove .mean from column and row names.
colnames(cm) <- rownames(cm) <- sapply(colnames(cm), function(s) gsub(".mean", "", s))
# Order variables by 1st principal component (PCA later in the course!)
corrplot(cm, order = "FPC", tl.cex = 0.5, tl.col = "black")

@@

Looking at the numeric values, we see that the measurements at different heights have strong positive correlation. Because of this, it is

```{r correlation, message=FALSE}
